### 2018-04-29 paper/security-analysis.tex
Adds more to security analysis (fixes #34)
Another thing for the security analysis

@@

>>>>

Alice wants to prevent Bob from learning which are her devices. Bob is allowed 
to infer the behaviour of devices in the global device swarm, a file transfer 
from Alice should not give Bob any information about which devices are Alice's.

We also prevent Carol and David to know that Alice and Bob exchanged a file. 
They forwarded unknown messages.

@@

Since we choose a new key for every file, we have forward secrecy between files.
\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
sent to Bob.
